---
title: "R Markdown Presentation & Ploty"
author: "daisuke ohnuki"
date: "2/16/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE,message=FALSE,warning=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	cache = TRUE,
	tidy = TRUE,
	tidy.opts = list(width.cutoff = 60)
)
```

## Synopsis {.smaller}

Following instructions have been given for the assignment -   

1. Create a web page presentation using R Markdown that features a plot created with Plotly.  
2. Host your webpage on either RPubs, GitHub Pages, or NeoCities.   
3. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly.



## Data Processing for Plot  : Heatmap R Code{.smaller}

```{r results='hide'}
library(datasets);library(plotly);library(reshape2)
data("airquality") ## Load the airquality dataset
airquality$Month=as.factor(airquality$Month) ## Convert Month to factor
ozone_daily=airquality[,c(1,5,6)] ## Extract Ozone, Month and Day columns
## Convert Long format to Wide for input to Heatmap
ozone_daily=dcast(ozone_daily,Day~Month,value.var = "Ozone") 
ozone_daily=as.matrix(ozone_daily[,-1]) ## Convert to Matrix
colnames(ozone_daily)=c("May","June","July","August","September")
## Plotly command
plot_ly(z=ozone_daily,colorscale="Hot",x=colnames(ozone_daily),type="heatmap",colorbar = list(title = "Ozone Levels (parts per billion)"))%>%layout(title = "Daily Ozone Levels in New York, May to September 1973", xaxis = list(title = "Month"),yaxis = list(title = "Day"))
```

## Plotly - Interactive Plot 1: Heatmap

```{r echo=FALSE}
library(datasets);library(plotly);library(reshape2)
data("airquality") ## Load the airquality dataset
airquality$Month=as.factor(airquality$Month) ## Convert Month to factor
ozone_daily=airquality[,c(1,5,6)] ## Extract Ozone, Month and Day columns
## Convert Long format to Wide for input to Heatmap
ozone_daily=dcast(ozone_daily,Day~Month,value.var = "Ozone") 
ozone_daily=as.matrix(ozone_daily[,-1]) ## Convert to Matrix
colnames(ozone_daily)=c("May","June","July","August","September")
## Plotly command
plot_ly(z=ozone_daily,colorscale="Hot",x=colnames(ozone_daily),type="heatmap",colorbar = list(title = "Ozone Levels (parts per billion)"))%>%layout(title = "Daily Ozone Levels in New York, May to September 1973", xaxis = list(title = "Month"),yaxis = list(title = "Day"))
```


